Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-25 GWLDCII.tex
fixed layout and floats

 % used for showing which propagator assigns to which vertex in the last section
\pgfmathsetmacro{\arrowangle}{90}
\tikzstyle{propassignment} = [->,shorten >=2pt,thick]

@@

\title{Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators}
\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
%\date{}

@@

\begin{figure}[h]
\[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture}\]

@@

\begin{dfn}\label{admisdfn}
A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if:
\begin{enumerate}
\item $|V| \geq |\cP| + 4$.
\item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
\item There does not exist a pair of crossing propagators: that is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
\end{enumerate}
 \end{dfn}

@@

\begin{figure}[h!]
\[\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
\draw (1,0) grid (2,3);
\draw (2,1) grid (4,3);
\draw (4,2) grid (5,3);
\draw[dotted] (2,0) -- (5,0) -- (5,2);

\node at (5.15,2.5) {\footnotesize$1$};
\node at (4.5,1.85) {\footnotesize$2$};
\node at (4.15,1.5) {\footnotesize$3$};
\node at (3.5,0.85) {\footnotesize$4$};
\node at (2.5,0.85) {\footnotesize$5$};
\node at (2.15,0.5) {\footnotesize$6$};
\node at (1.5,-0.15) {\footnotesize$7$};
%\node at (0.5,-0.15) {\footnotesize$8$};
\end{tikzpicture}
\qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
\draw (1,0) grid (2,3);
\draw (2,1) grid (4,3);
\draw (4,2) grid (5,3);
\draw[dotted] (2,0) -- (6,0) -- (6,3) -- (5,3);

\node at (5.5,2.85) {\footnotesize$1$};
\node at (5.15,2.5) {\footnotesize$2$};
\node at (4.5,1.85) {\footnotesize$3$};
\node at (4.15,1.5) {\footnotesize$4$};
\node at (3.5,0.85) {\footnotesize$5$};
\node at (2.5,0.85) {\footnotesize$6$};
\node at (2.15,0.5) {\footnotesize$7$};
\node at (1.5,-0.15) {\footnotesize$8$};
%\node at (0.5,-0.15) {\footnotesize$9$};
\end{tikzpicture}
\]
\caption{Row and column numbering for a Young diagram with $k = 3$, $n = 7$ (left) and $k = 3$, $n = 8$ (right). The top left box has coordinates $(1,7)$ in the left diagram, and $(2,8)$ in the right diagram.}
\label{fig:row column numbering}
\end{figure}

@@

\begin{eg}
Let $W$ be the Wilson loop diagram from Figure \ref{fig:ex of WLD}, reproduced here for convenience.  \[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{0}{4}{0}{\footnotesize \qquad \ $p$}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture}\]

Let $p$ be the propagator $p = (1, 4)$. Then $\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \}$ and $\cP_{out}(p, <_4) = \{(2,4) \}$
\end{eg}

@@

\begin{rmk}\label{rem:props of length 2 and 3} 
  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
 \begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.  By the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in the interval $[i,j]$ supports at least one propagator, then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
\end{enumerate}
\end{rmk}

\begin{figure}[h]
\[
\begin{tikzpicture}[baseline=(current bounding box.north)]
  \begin{scope}
  \drawWLDfragment[7]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 1.43*\step:\zero+6.6*\step:\radius)
  \newnode{1}{}
  \newnode{3.55}{}
  \newnode{4.45}{}
  \newnode{7}{}
    \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
  \newpropbend{1.3}{6.7}{20}
  \newpropbend{2.9}{5.1}{45}
  \end{scope}
  \node[align=center] at (\zero + 4*\step:\radius*1.43) {\footnotesize \em $\leq 6$ vertices in the highlighted \\ \footnotesize \em region and no other propagators\\ \footnotesize \em in the highlighted region};
\end{scope}
\end{tikzpicture}
\qquad \qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.north)]
  \begin{scope}
  \drawWLDfragment[7]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 3.67*\step:\zero+4.43*\step:\radius)
  \newnode{1}{i}
  \newnode[below]{2}{i+1\ \ \ }
  \newnode[below]{3}{i+2}
  \newnode[below]{5}{j+1}
  \newnode[below]{6}{\quad j+2}
  \newnode[right]{7}{j+3}
      \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
  \newpropbend{1.35}{3.6}{55}
  \newpropbend{4.4}{6.6}{55}
  \end{scope}
  \node[align=center] at (\zero + 4*\step:\radius*1.5) {\footnotesize \em $\leq 2$ vertices in the highlighted \\ \footnotesize \em region, and  no other propagators \\ \em \footnotesize end in the highlighted region};
\end{scope}
\end{tikzpicture}
\]
\caption{The two configurations described in Lemma~\ref{lem sian}; every weakly admissible Wilson loop diagram with no non-supporting vertices admits at least one example of at least one of these configurations.}\label{fig: small configs}
\end{figure}

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
	\begin{scope}
	\drawWLDfragment[10]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\centerarc[linehighlight](0,0)(\zero + 1.5*\step:\zero + 2.35*\step:\radius)
	\newnode{1}{}
	\newnode{3}{}
	\newnode{4}{}
	\newnode{5}{}
	\newnode[below]{9}{i_1}
	\newnode{10}{}
	\newprop[midway,above]{1.4}{9.5}{\footnotesize $q_1$}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
		\newpropbend{2.3}{4.7}{60}
		\node at (\zero + 3.5*\step:\radius*0.78) {\footnotesize $p_1$};
	\end{scope}
\node[align = center] at (\zero +1.7*\step:\radius*1.4) {\footnotesize \em 0, 1, or 2 \\ \footnotesize \em vertices in \\ \footnotesize \em this region};
\node[gray] at (\zero + 10*\step:\radius*0.4) {\footnotesize$\cP_{in}(q_1,<_{i_1})$};
\node[gray] at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $\cP_{out}(q_1,<_{i_1})$};
\end{scope}
\end{tikzpicture}
\]
\caption{The base case of the induction in Lemma~\ref{lem sian}.}\label{fig base case lem sian} \end{figure}

@@

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
  \begin{scope}
  W' = \drawWLDfragment[12]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \newnode[left]{1}{i}
  \newnode[below]{4}{j}
  \newnode{5}{}
  \newnode{6}{}
  \newnode{7}{}
  \newnode{8}{}
  \newnode{9}{}
  \newnode{11}{}
  \newnode[right]{12}{l+1}
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
    \newpropbend{5.3}{7.6}{80}
    \node at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $r$};
    \newprop[midway,left]{8.5}{-4}{}
    \node at (\zero + 8.15*\step:\radius*0.5) {\footnotesize $p$};
    \newprop[midway]{11.5}{-4}{}
    \node at (\zero + 12.2*\step:\radius*0.7) {\footnotesize $q$};
  \end{scope}
\end{scope}
\end{tikzpicture}
\qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.east)]
  V' = \begin{scope}
  \drawWLDfragment[12]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \newnode[left]{2}{m}
  \newnode[below]{4}{j}
  \newnode{5}{}
  \newnode{6}{}
  \newnode{7}{}
  \newnode{8}{}
  \newnode{9}{}
  \newnode{11}{}
  \newnode[right]{12}{l+1}
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
    \newpropbend{5.3}{7.6}{80}
    \node at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $r$};
    \newprop[midway,left]{8.5}{22}{}
    \node at (\zero + 8.5*\step:\radius*0.5) {\footnotesize $s$};
    \newprop[midway]{11.5}{21}{}
    \node at (\zero + 11.8*\step:\radius*0.8) {\footnotesize $t$};
  \end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$. Note that propagators such as $r$ which have {\em both} ends inside the region of interest must be identical in both diagrams.}\label{fig:locally identical}
\end{figure}

@@

\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate = -18]
	\begin{scope}
	\drawWLDfragment[20]{2}{1}
	%\drawnumbers % use this to debug
	\newnode[left]{4}{I_i(p) = i-1}
	\newnode[left]{5}{i}
	\newnode[left]{7}{c}
	\newnode[left]{8}{}
	\newnode[right]{15}{b}
	\newnode[right]{16}{b+1}
	\newprop[midway,above]{4.7}{15.7}{\scriptsize $p$}
	\newprop[midway,below]{7.5}{15.3}{\scriptsize $q$}
      \draw[smallpropagator,light-gray] (\zero +\step *4.3:\radius*1) -- (90:\radius*0.5); 
	\node at (270+18:\radius*1.5) {\em Case 1};
	% \begin{scope}
	% \clip (\zero + 5*\step:\radius*1.1) rectangle (90:\radius*0.8);
	% \draw[smallpropagator,color=gray] (\zero+4.5*\step:\radius) -- (\zero + 19*\step:\radius);
	% \end{scope}
		\end{scope}
	\end{tikzpicture}
\qquad \qquad 
	\begin{tikzpicture}[baseline=(current bounding box.east),rotate = 36]
	\begin{scope}
	\drawWLDfragment[20]{2}{1}
	%\drawnumbers % use this to debug
	\newnode[left]{4}{a}
	\newnode[left]{5}{}
	\newnode[left]{7}{}
	\newnode[left]{8}{}
	\newnode[right]{15}{b}
	\newnode[right]{16}{b+1 = I_i(p)}
	\newnode[right]{11}{d}
	\newnode[below]{12}{}
	\newnode[left]{2}{i}
	\newprop[midway,above]{4.5}{15.7}{\scriptsize $p$}
		\node at (270-36:\radius*1.5) {\em Case 2};
	\begin{scope}
	\clip (0,0) circle (\radius);
	%q
	\draw[smallpropagator] (\zero+11.5*\step:\radius*1.2) to [bend left = 45] (\zero + 15.5*\step:\radius*1.2); 
	\node at (\zero + 13.5*\step:\radius*0.55) {\scriptsize $q$};
	%r
	\draw[smallpropagator] (\zero+7.5*\step:\radius*1.2) to [bend left = 45] (\zero + 11.4*\step:\radius*1.2);
	\node at (\zero + 9.5*\step:\radius*0.55) {\scriptsize $r$};

	\end{scope}
		\end{scope}
	\end{tikzpicture}
\] 
\caption{The two types of configuration that would (in theory) allow the propagator $p$ to contribute its $<_i$-maximal support vertex to $I_i$.}
\label{fig:no fourth vertex}
\end{figure}
In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$. Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2. Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.

@@

@@

@@

\begin{tabular}{lll}
% case 1
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\drawWLDfragment[8]{3}{0.3} % draws the arc and sets up the parameters
	%\drawnumbers % use this to debug
	% next two lines draw the highlighted regions
	\centerarc[linehighlight](0,0)(\zero + 1.85*\step:\zero + 4.4*\step:\radius)
	\centerarc[linehighlight](0,0)(\zero + 6.75*\step:\zero + 7.4*\step:\radius)
	% labels explaining the highlighted regions
	\node[align = center] at (\zero + 2.7*\step:\radius*1.3) {\em \footnotesize 1 or 2 vertices \\[3pt] \em \footnotesize in this region};
	\node[align = center] at (\zero + 7.5*\step:\radius*1.4) {\em \footnotesize 0 or 1 vertices \\[3pt]\em \footnotesize in this region};
	\begin{scope} % this scope draws the propagators and their labels
		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
		%q
		\draw[smallpropagator] (\zero+1.65*\step:\radius*1.1) to [bend left = 40] (\zero + 7.4*\step:\radius*1.1); 
		%p
		\draw[smallpropagator] (\zero+4.3*\step:\radius*1.1) to [bend left = 55] (\zero + 6.8*\step:\radius*1.1); 
		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
		\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
		\node at (\zero + 5.5*\step:\radius*0.8){\footnotesize $p$};
	% draw the nodes
	\newnode[left]{1}{i}
	\newnode[right]{8}{j+1}
	\newnode[below]{5}{}
	\newnode[below]{6}{}
% case label
\node at (270:\radius*0.2) {\em Case 1};
%
%
%
& \qquad \qquad &
%
%
%
% case 2
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\drawWLDfragment[8]{3}{0.3} % draw arc
	%\drawnumbers % use this to debug
	% highlighted regions
	\centerarc[linehighlight](0,0)(\zero + 1.85*\step:\zero + 2.4*\step:\radius)
	\centerarc[linehighlight](0,0)(\zero + 4.75*\step:\zero + 7.4*\step:\radius)

>>>>

 % used for showing which propagator assigns to which vertex in the last section
\pgfmathsetmacro{\arrowangle}{90}
\pgfmathsetmacro{\diagramscale}{1.3}
\tikzstyle{propassignment} = [->,shorten >=2pt,thick]

@@

\title{Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators}
\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
\date{}

@@

\begin{figure}[h]
\[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{2}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture}\]

@@

\begin{dfn}\label{admisdfn}
A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if:
\begin{enumerate}
\item $|V| \geq |\cP| + 4$.
\item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
\item There are no crossing propagators: that is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
\end{enumerate}
 \end{dfn}

@@

\begin{figure}
\[\begin{tikzpicture}
\node at (0,3.5) {}; % purely for spacing reasons
\node at (0,-0.5) {}; % purely for spacing reasons
\draw (1,0) grid (2,3);
\draw (2,1) grid (4,3);
\draw (4,2) grid (5,3);
\draw[dotted] (2,0) -- (5,0) -- (5,2);

\node at (5.15,2.5) {\footnotesize$1$};
\node at (4.5,1.85) {\footnotesize$2$};
\node at (4.15,1.5) {\footnotesize$3$};
\node at (3.5,0.85) {\footnotesize$4$};
\node at (2.5,0.85) {\footnotesize$5$};
\node at (2.15,0.5) {\footnotesize$6$};
\node at (1.5,-0.15) {\footnotesize$7$};
%\node at (0.5,-0.15) {\footnotesize$8$};

\begin{scope}[shift = {(7,0)}]
\draw (1,0) grid (2,3);
\draw (2,1) grid (4,3);
\draw (4,2) grid (5,3);
\draw[dotted] (2,0) -- (6,0) -- (6,3) -- (5,3);

\node at (5.5,2.85) {\footnotesize$1$};
\node at (5.15,2.5) {\footnotesize$2$};
\node at (4.5,1.85) {\footnotesize$3$};
\node at (4.15,1.5) {\footnotesize$4$};
\node at (3.5,0.85) {\footnotesize$5$};
\node at (2.5,0.85) {\footnotesize$6$};
\node at (2.15,0.5) {\footnotesize$7$};
\node at (1.5,-0.15) {\footnotesize$8$};
%\node at (0.5,-0.15) {\footnotesize$9$};
\end{scope}
\end{tikzpicture}
\]
\caption{Row and column numbering for a Young diagram with $k = 3$, $n = 7$ (left) and $k = 3$, $n = 8$ (right). The top left box has coordinates $(1,7)$ in the left diagram, and $(2,8)$ in the right diagram.}
\label{fig:row column numbering}
\end{figure}

@@

\begin{eg}
Let $W$ be the Wilson loop diagram from Figure \ref{fig:ex of WLD}, reproduced here for convenience.  \[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{2}
	\drawnumbers
	\drawlabeledprop{1}{0}{4}{0}{\footnotesize \qquad \ $p$}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture}\]

Let $p$ be the propagator $p = (1, 4)$. Then $(p,<_4)$ indicates that we are viewing $p$ as being directed from 4 to 1, and we have
\begin{gather*}\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \};\\
\cP_{out}(p, <_4) = \{(2,4) \}. \end{gather*}
\end{eg}

@@

\begin{rmk}\label{rem:props of length 2 and 3} 
  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
  \vspace{-0.5em}
 \begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.  By the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in the interval $[i,j]$ supports at least one propagator, then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
\end{enumerate}
\end{rmk}

\begin{figure}
\[
\begin{tikzpicture}[scale = 0.8,baseline=(current bounding box.north)]
  \begin{scope}
  \drawWLDfragment[7]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 1.48*\step:\zero+6.64*\step:\radius)
  \newnode{1}{}
  \newnode{3.55}{}
  \newnode{4.45}{}
  \newnode{7}{}
    \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
  \newpropbend{1.3}{6.7}{20}
  \newpropbend{2.9}{5.1}{45}
  \end{scope}
  \node[align=center] at (\zero + 4*\step:\radius*1.43) {\footnotesize \em $\leq 6$ vertices in the highlighted \\ \footnotesize \em region and no other propagators\\ \footnotesize \em in the highlighted region};
\end{scope}

  \begin{scope}[shift = {(9,0)}]
  \drawWLDfragment[7]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 3.67*\step:\zero+4.47*\step:\radius)
  \newnode{1}{i}
  \newnode[below]{2}{i+1\ \ \ }
  \newnode[below]{3}{i+2}
  \newnode[below]{5}{j+1}
  \newnode[below]{6}{\quad j+2}
  \newnode[right]{7}{j+3}
      \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
  \newpropbend{1.35}{3.6}{55}
  \newpropbend{4.4}{6.6}{55}
  \end{scope}
  \node[align=center] at (\zero + 4*\step:\radius*1.5) {\footnotesize \em $\leq 2$ vertices in the highlighted \\ \footnotesize \em region, and  no other propagators \\ \em \footnotesize end in the highlighted region};
\end{scope}
\end{tikzpicture}
\]
\caption{The two configurations described in Lemma~\ref{lem sian}; every weakly admissible Wilson loop diagram with no non-supporting vertices admits at least one example of at least one of these configurations.}\label{fig: small configs}
\end{figure}

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
  \vspace{-0.5em}
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

@@

\begin{figure}[h]
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
  \begin{scope}
  \drawWLDfragment[10]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \centerarc[linehighlight](0,0)(\zero + 1.5*\step:\zero + 2.35*\step:\radius)
  \newnode{1}{}
  \newnode{3}{}
  \newnode{4}{}
  \newnode{5}{}
  \newnode[below]{9}{i_1}
  \newnode{10}{}
  \newprop[midway,above]{1.4}{9.5}{\footnotesize $q_1$}
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
    \newpropbend{2.3}{4.7}{60}
    \node at (\zero + 3.5*\step:\radius*0.78) {\footnotesize $p_1$};
  \end{scope}
\node[align = center] at (\zero +1.7*\step:\radius*1.4) {\footnotesize \em 0, 1, or 2 \\ \footnotesize \em vertices in \\ \footnotesize \em this region};
\node[gray] at (\zero + 10*\step:\radius*0.4) {\footnotesize$\cP_{in}(q_1,<_{i_1})$};
\node[gray] at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $\cP_{out}(q_1,<_{i_1})$};
\end{scope}
\end{tikzpicture}
\]
\caption{The base case of the induction in Lemma~\ref{lem sian}.}\label{fig base case lem sian} \end{figure}

@@

\begin{figure}[h]
\[
\begin{tikzpicture}[scale = 0.9,baseline=(current bounding box.east)]
  \begin{scope}
  \drawWLDfragment[12]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \node at (0:0) {}; % purely for spacing purposes
  \newnode[left]{1}{i}
  \newnode[below]{4}{j}
  \newnode{5}{}
  \newnode{6}{}
  \newnode{7}{}
  \newnode{8}{}
  \newnode{9}{}
  \newnode{11}{}
  \newnode[right]{12}{l+1}
  \node at (\zero + 3*\step:\radius*0.65) {\Large $W'$};
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
    \newpropbend{5.3}{7.6}{80}
    \node at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $r$};
    \newprop[midway,left]{8.5}{-4}{}
    \node at (\zero + 8.15*\step:\radius*0.5) {\footnotesize $p$};
    \newprop[midway]{11.5}{-4}{}
    \node at (\zero + 12.2*\step:\radius*0.7) {\footnotesize $q$};
  \end{scope}
\end{scope}

  \begin{scope}[shift = {(9,0)}]
  \drawWLDfragment[12]{3}{0.4} 
  %\drawnumberspartial % use this to debug
  \newnode[left]{2}{m}
  \newnode[below]{4}{j}
  \newnode{5}{}
  \newnode{6}{}
  \newnode{7}{}
  \newnode{8}{}
  \newnode{9}{}
  \newnode{11}{}
  \newnode[right]{12}{l+1}
  \node at (\zero + 4*\step:\radius*0.5) {\Large $V'$};
  \begin{scope}
    \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
    \newpropbend{5.3}{7.6}{80}
    \node at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $r$};
    \newprop[midway,left]{8.5}{22}{}
    \node at (\zero + 8.5*\step:\radius*0.5) {\footnotesize $s$};
    \newprop[midway]{11.5}{21}{}
    \node at (\zero + 11.8*\step:\radius*0.8) {\footnotesize $t$};
  \end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$. Note that propagators such as $r$ which have {\em both} ends inside the region of interest must be identical in both diagrams.}\label{fig:locally identical}
\end{figure}

@@

In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$. Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2. Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.

@@

\begin{figure}[h]
\[
\begin{tikzpicture}[baseline=(current bounding box.east),rotate = -18]
  \begin{scope}
  \drawWLDfragment[20]{2.2}{1}
  %\drawnumbers % use this to debug
  \node at (108:\radius*1.2) {}; % spacing
  \newnode[left]{4}{I_i(p) = i-1}
  \newnode[left]{5}{i}
  \newnode[left]{7}{c}
  \newnode[left]{8}{}
  \newnode[right]{15}{b}
  \newnode[right]{16}{b+1}
  \newprop[midway,above]{4.7}{15.7}{\scriptsize $p$}
  \newprop[midway,below]{7.5}{15.3}{\scriptsize $q$}
      %\draw[smallpropagator,light-gray] (\zero +\step *4.3:\radius*1) -- (90:\radius*0.5); 
  \node at (270+18:\radius*1.5) {\em Case 1};
  % \begin{scope}
  % \clip (\zero + 5*\step:\radius*1.1) rectangle (90:\radius*0.8);
  % \draw[smallpropagator,color=gray] (\zero+4.5*\step:\radius) -- (\zero + 19*\step:\radius);
  % \end{scope}
    \end{scope}
  \end{tikzpicture}
\qquad \qquad 
  \begin{tikzpicture}[baseline=(current bounding box.east),rotate = 36]
  \begin{scope}
  \drawWLDfragment[20]{2.2}{1}
  %\drawnumbers % use this to debug
  \newnode[left]{4}{a}
  \newnode[left]{5}{}
  \newnode[left]{7}{}
  \newnode[left]{8}{}
  \newnode[right]{15}{b}
  \newnode[right]{16}{b+1 = I_i(p)}
  \newnode[right]{11}{d}
  \newnode[below]{12}{}
  \newnode[left]{2}{i}
  \newprop[midway,above]{4.5}{15.7}{\scriptsize $p$}
    \node at (270-36:\radius*1.5) {\em Case 2};
  \begin{scope}
  \clip (0,0) circle (\radius);
  %q
  \draw[smallpropagator] (\zero+11.5*\step:\radius*1.2) to [bend left = 45] (\zero + 15.5*\step:\radius*1.2); 
  \node at (\zero + 13.5*\step:\radius*0.55) {\scriptsize $q$};
  %r
  \draw[smallpropagator] (\zero+7.5*\step:\radius*1.2) to [bend left = 45] (\zero + 11.4*\step:\radius*1.2);
  \node at (\zero + 9.5*\step:\radius*0.55) {\scriptsize $r$};

  \end{scope}
    \end{scope}
  \end{tikzpicture}
\] 
\caption{The two types of configuration that would (in theory) allow the propagator $p$ to contribute its $<_i$-maximal support vertex to $I_i$.}
\label{fig:no fourth vertex}
\end{figure}

@@

% there's some big multiline displayed equations in this proof, so we temporarily enable \allowdisplaybreaks
\begingroup
\allowdisplaybreaks

@@

\begin{figure}
\[\begin{tikzpicture}[baseline=(current bounding box.east)]
% case 1
	\begin{scope}
	\drawWLDfragment[8]{3}{0.3} % draws the arc and sets up the parameters
	%\drawnumbers % use this to debug
	% next two lines draw the highlighted regions
	\centerarc[linehighlight](0,0)(\zero + 1.85*\step:\zero + 4.4*\step:\radius)
	\centerarc[linehighlight](0,0)(\zero + 6.75*\step:\zero + 7.4*\step:\radius)
	% labels explaining the highlighted regions
	\node[align = center] at (\zero + 2.7*\step:\radius*1.3) {\em \footnotesize 1 or 2 vertices \\[3pt] \em \footnotesize in this region};
	\node[align = center] at (\zero + 7.5*\step:\radius*1.4) {\em \footnotesize 0 or 1 vertices \\[3pt]\em \footnotesize in this region};
	\begin{scope} % this scope draws the propagators and their labels
		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
		%q
		\draw[smallpropagator] (\zero+1.65*\step:\radius*1.1) to [bend left = 40] (\zero + 7.4*\step:\radius*1.1); 
		%p
		\draw[smallpropagator] (\zero+4.3*\step:\radius*1.1) to [bend left = 55] (\zero + 6.8*\step:\radius*1.1); 
		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
		\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
		\node at (\zero + 5.5*\step:\radius*0.8){\footnotesize $p$};
	\end{scope}
	% draw the nodes
	\newnode[left]{1}{i}
	\newnode[right]{8}{j+1}
	\newnode[below]{5}{}
	\newnode[below]{6}{}
% case label
\node at (270:\radius*0.2) {\em Case 1};
\end{scope}
